Presentation Plan\\ FF-Replan: \& RFF\@: Exploiting classical AI planning for uncertain and probabilistic domains

### 2014-03-02 presentation-plan/Plan_presentation_monday.tex
Short Classical Planner description

@@

>>>>

Classical Planners do not take uncertainties into account. Classical Planners
are deterministic.

STRIPS is considered one of the first planning algorithms and
representations.~\cite{lavalle2006planning}. It is a very simple logic based
only on literal. It's very nice to describe planning problems in a
descriptive way that closely corresponds to the application. Also due to the
operator definition (action/preconditions) it's possible to describe complex

@@

With states and actions, it's easy to see that a planning problem can be
represented by a directed graph, where the states are the nodes, and the
actions are the edges that connect states. The planning problem is now
a search problem from the root to the goal states.

A well known planner that uses a planning graph is Graphplan.
[However that seems, after some investigation, to work in an interesting
different way\ldots]
